\documentclass[11pt]{article}
%------------------------Dimensions--------------------------------------------
\topmargin=0.0in %length of margin at the top of the page (1 inch added by default)
\oddsidemargin=0.0in %length of margin on sides for odd pages
\evensidemargin=0in %length of margin on sides for even pages
\textwidth=6.5in %How wide you want your text to be
\marginparwidth=0.5in
\headheight=0pt %1in margins at top and bottom (1 inch is added to this value by default)
\headsep=0pt %Increase to increase white space in between headers and the top of the page
\textheight=9.0in %How tall the text body is allowed to be on each page

\usepackage{longtable}
\usepackage{tabu}
\usepackage{titlesec}
\usepackage{changepage}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage[document]{ragged2e}
\titleformat{\section}
    {\normalfont \Large \bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]


\newcommand{\datewidth}{0.2\textwidth}
\newcommand{\descwidth}{0.755\textwidth}
\renewcommand{\familydefault}{\sfdefault}
\begin{document}
\pagenumbering{gobble}

%Use link for power words
%https://hwpi.harvard.edu/files/ocs/files/undergrad_resumes_and_cover_letters.pdf

\centerline{{\Huge Jacob Imola}}
\noindent Website: \href{https://jimola.github.io/}{https://jimola.github.io/} \hfill Email: \href{mailto:jimola@eng.ucsd.edu}{jimola@eng.ucsd.edu}

\section*{Education}
\tabulinesep=^2mm_2mm
\begin{tabu}{X[4, l] X[1, l]}
	\setlength{\extrarowsep}{3mm}
  \textbf{University of California, San Diego} \newline
  PhD Candidate in Computer Science, Expected Graduation 2023 \newline
  Advisor: Prof. Kamalika Chaudhuri 
	&
  2018-Now \\
  \textbf{Carnegie Mellon University} \newline
  B.S. in Computer Science, Minor in Mathematics \newline
  Advisor: Prof. Jean Yang \newline
  GPA: 3.85/4.00
	&
  2014-2018 \\
\end{tabu}

\section*{Research Vision}
My primary focus is differential privacy, where I 
am intrigued by questions like how to define privacy for graphs and how to improve the performance of private graph algorithms.
I am also interested in the connections between information theory and privacy, such as strong composition and privacy-utility bounds.

I am becoming more interested in theoretical aspests of trustworthy machine learning/statistics, such as how to take a well-known 
problem like clustering and design algorithms which are private, robust, resistant to data poisoning, etc.
\section*{Conference Publications}
\begin{itemize}
	\setlength\itemsep{-0.3em}
	\item Jacob Imola, Takao Murakami, and Kamalika Chaudhuri.
		\textit{\href{https://arxiv.org/abs/2205.01429.pdf}{Differentially Private Triangle and 4-Cycle Counting in the Shuffle Model}}. In \textbf{CCS 2022}. 
	\item Jacob Imola, Shiva Kasiviswanathan, Stephen White, Abhinav Aggarwal, Nathanael Teissier.
		\textit{\href{https://openreview.net/pdf?id=B0l8-wLjql5}{Balancing Utility and Scalability in Metric Differential Privacy}}. In \textbf{UAI 2022}.
	\item 
		Jacob Imola, Takao Murakami, and Kamalika Chaudhuri.
		\textit{\href{https://arxiv.org/abs/2110.06485}{Communication-Efficient Triangle Counting under Local Differential Privacy}}. In \textbf{USENIX Security 2022}.
	\item 
		Jacob Imola, Takao Murakami, and Kamalika Chaudhuri.
		\textit{\href{https://arxiv.org/abs/2010.08688}{Locally Differentially Private Analysis of Graph Statistics}}. In \textbf{USENIX Security 2021}.
	\item
		Kamalika Chaudhuri, Jacob Imola, and Ashwin Machanavajjhala.
		\textit{\href{https://arxiv.org/abs/1907.02159}{Capacity Bounded Differential Privacy}}.
	  In \textbf{NeurIPS 2019}.
\end{itemize}

\section*{Preprints}
\begin{itemize}
	\setlength\itemsep{-0.3em}
	\item
		Jacob Imola, Amrita Roy Chowdhury, and Kamalika Chaudhuri.
		\textit{\href{https://arxiv.org/pdf/2210.14376.pdf}{Robustness of Locally Differentially Private Graph Analysis Against Poisoning}}. 2022
	\item 
		Robi Bhattacharjee, Jacob Imola, Michal Moshkovitz, and Sanjoy Dasgupta.
		\textit{\href{https://arxiv.org/abs/2102.09101}{Online $k$-means Clustering on Arbitrary Data Streams}}. 2022
\end{itemize}

\section*{Other Publications}
\begin{itemize}
	\setlength\itemsep{-0.3em}
	\item
		Jacob Imola and Kamalika Chaudhuri.
		\textit{\href{https://arxiv.org/abs/2105.10594}{Privacy Amplification Via Bernoulli Sampling}}. In \textbf{TPDP Workshop at ICML 2021}.
\end{itemize}


\section*{Work Experience}
%\tabulinesep=^2mm_2mm
\begin{tabu}{X[4, l] X[1, l]}
	\textbf{Research Intern}, Google \newline
	Host: Alessandro Epasto
	\begin{itemize}
	\setlength\itemsep{-0.3em}
	\item Developed hierarchical clustering algorithms under differential privacy; paper in preparation.
	\item Implemented private graph building pipeline in C++.
	\end{itemize}
&
	June - September 2022 \\
	\textbf{Research Intern}, Amazon \newline
	Host: Abhinav Aggarwal 
	\begin{itemize}
		\setlength\itemsep{-0.3em}
		\item Optimized utility for private text-release mechanism.
		\item First author of paper \textit{\href{https://openreview.net/pdf?id=B0l8-wLjql5}{Balancing Utility and Scalability in Metric Differential Privacy}}. 
		\item Source at \href{https://bitbucket.org/jjimola/dptextgeometry/}{https://bitbucket.org/jjimola/dptextgeometry/}
	\end{itemize}
&
	June - September 2021 \\
\end{tabu}

\section*{Teaching Experience}
\tabulinesep=^2mm_2mm
\begin{tabu}{X[4,l] X[1,l]}
  \textbf{High School Research Mentor} \newline
    Summer STEM Institute 
  & June 2021-July 2021 \\
	\textbf{Teaching Assistant} \newline
    CSE 151A: Introduction to AI: A Statistical Approach 
  & January 2021-March 2021 \\
  \textbf{Teaching Assistant} \newline
    CSE 151A: Introduction to AI: A Statistical Approach 
  & January 2020-March 2020 \\
\end{tabu}

\section*{Service}
\begin{itemize}
	\item Mentor for UCSD Graduate Women in Computer Science, 2021 \& 2022.
	\item Reviewer for NeurIPS 2022, ICML 2022, NeurIPS 2021, PRIML Workshop at NeurIPS 2021.
\end{itemize}

\section*{Computer Skills}
\begin{tabular}{rl}
  Programming Languages: & C++, Python, OCaml, Java, R, Javascript, SQL, \LaTeX \\
  Industrial Tools: & Numpy/Scipy, Scikit-learn, Sage.
\end{tabular}


\section*{Other Experience}
\tabulinesep=^2mm_2mm
\begin{tabu}{X[4,l] X[1,l]}
	\textbf{Summer Intern} \newline
    Quantitative Market Researcher at Jump Trading
  & June 2017-August 2017 \\
	\textbf{Summer Intern} \newline
    Software Engineer at Salesforce
  & June 2016-August 2016 \\
\end{tabu}

\section*{Academic Honors}

\begin{tabular}{rl}
  2018 & Senior Thesis Honors Program at CMU \\
  2016 & William Lowell Putnam Math Competition Honorable Mention \\
  2015 & ACM-ICPC Regional Programming Competition Team Member
\end{tabular}
\end{document}
